\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-29 document/XSGRB_sample.tex
Adding GRB101219A and GRB101219B

	\subsection{GRB100316D (z = 0.059)}
	The data presented here also formed the basis of GCN \#
	10512\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10512.gcn3}}, GCN \#
	10513\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10513.gcn3}}, GCN \#
	10543\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10543.gcn3}} and is published
	in \citet{Bufano2012} and \citet{Starling2011}. This GRB is very close by and
	has an associated SN and has therefore undergone intense follow-up. The data
	presented here consists of a subset of the entire VLT/X-shooter campaign,
	covering the four first observing days while the afterglow still contributes
	significantly to the total emission. The first observations started 10 hours
	after the burst, before the SN was discovered, and targeted the star-forming
	'A'-region\citep{Starling2011}, not the GRB. A very rich spectrum containing a
	multitude of emission lines puts the host at $z = 0.059$. For three consequtive
	nights, 58, 79 and 101 hours after the \textit{Swift} trigger, the afterglow
	was observed as it transitioned into the spectrum of a high-velocity Ic-BL SN.
	The observations taken 79 and 101 hours after the burst are taken under
	programme 084.D-0265(A) (PI: Benetti), but with a similar setup to first two
	observations.

@@

	\subsection{GRB100901A(z=1.408)}
	The data presented here has been published in \citet{Hartoog2013}. Because of
	the unusual lingering brightness of this GRB, 2.4s of observations taken 65.98
	hours after the GRB trigger still reveals an afterglow continuum visible across
	the entire spectral coverage of X-shooter. Absorption lines from a wide range
	ion put the redshift at $z=1.408$, with intervening absorption systems at $z =
	1.3147$ and $z = 1.3179$.

>>>>

	\subsection{GRB100316D (z = 0.059)}
	The data presented here also formed the basis of GCN \#
	10512\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10512.gcn3}}, GCN \#
	10513\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10513.gcn3}}, GCN \#
	10543\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10543.gcn3}} and is published
	in \citet{Bufano2012} and \citet{Starling2011}. This GRB is very close by and
	has an associated SN, SN2010bh, and has therefore undergone intense follow-up. The data
	presented here consists of a subset of the entire VLT/X-shooter campaign,
	covering the four first observing days while the afterglow still contributes
	significantly to the total emission. The first observations started 10 hours
	after the burst, before the SN was discovered, and targeted the star-forming
	'A'-region\citep{Starling2011}, not the GRB. A very rich spectrum containing a
	multitude of emission lines puts the host at $z = 0.059$. For three consequtive
	nights, 58, 79 and 101 hours after the \textit{Swift} trigger, the afterglow
	was observed as it transitioned into the spectrum of a high-velocity Ic-BL SN.
	The observations taken 79 and 101 hours after the burst are taken under
	programme 084.D-0265(A) (PI: Benetti), but with an identical setup to the first
	two observations.

@@

	\subsection{GRB100901A (z=1.408)}
	The data presented here has been published in \citet{Hartoog2013}. Because of
	the unusual lingering brightness of this GRB, 2.4s of observations taken 65.98
	hours after the GRB trigger still reveals an afterglow continuum visible across
	the entire spectral coverage of X-shooter. Absorption lines from a wide range
	ion put the redshift at $z=1.408$, with intervening absorption systems at $z =
	1.3147$ and $z = 1.3179$.

	\subsection{GRB101219A (z=0.718)}
	This data has not been published before. Starting 3.7 hours after the GRB
	trigger, 7.2 ks of exposure time reveals a very faint continuum in the visual
	and near-infrared, only visible when heavily binning the images. No redshift
	estimate is available from these observations.  Late-time Gemini-North
	observations reveal emission lines from the host at
	$z=0.718$\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/11518.gcn3}}.

	\subsection{GRB101219B (z=0.552)}
	The data presented here also formed the basis of GCN \#
	11579\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/11579.gcn3}} and is published
	in \citet{Sparre2011}.	The first observation, taken 11.6 hours after the burst
	trigger and lasting 4.8ks, reveals absorption from \mgii~and \mgi~in the host
	located at $z = 0.552$ on a featureless continuum visible across the entire
	coverage of X-shooter.  Subsequent observations taken 16 and 37 days after the
	trigger shows the fading spectral signature of a SN, SN2010ma.
